\documentclass{article}
\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=1in]{geometry}
\usepackage[colorlinks=true ,urlcolor=blue,urlbordercolor={0 1 1}]{hyperref}
\usepackage{xcolor}
\usepackage[parfill]{parskip}

\titleformat{\section}
{\huge\bfseries}
{}
{0em}
{}[\titlerule]
\begin{document}

\titleformat{\subsection}
{\bfseries\Large}
{$\bullet$}
{0em}
{}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}

\urlstyle{same}
\renewcommand{\maketitle}{\begin{center}{\huge\bfseries\theauthor}\vspace{.25em}

\href{mailto:jared.dyreson@gmail.com}{jared.dyreson@gmail.com} --- \url{https://JaredDyreson.github.io}

\end{center}}

\author{Jared Dyreson}
\maketitle

\section{Experience}
\subsection{Volunteer}
\begin{itemize}
	\item July 2010, Special Education classroom volunteer, Las Lomas Elementary School
	\item September 2010 to August 2017, Visual Performance Lead at Sojourners Church, Fullerton
	\item June 2015, Professional Photography Assistant for Joshua Scheide, Newport Beach Pier
	\item September 2015, Speech and Language Pathology volunteer, Las Lomas Elementary School
	\item Summer of 2016, NOC SELPA Intern; Olita and Carl E. Gilbert Elementary School for 150 hours
	\item Classroom Aide for Theresa Collar, Raymond Elementary School, September 2016 to May 2017
\end{itemize}
\subsection{Paid}
\begin{itemize}
	\item July 2017 to present, Starbucks Corporation. Reference available upon request.
\end{itemize}

\section{Education}

\subsubsection{Troy High School}

I have completed the necessary requirements mandated by the Troy Tech Program and have graduated from Troy High School in May of 2017. I have taken several ROP (Regional Occupation Program) classes including CAD Design, Art and Animation, Child Development and Principles of Teaching and Learning.

\subsubsection{College}

I am currently attending California State University Fullerton and pursing a Master's Degree in Computer Science. I intend to graduate in 2023.

\section{Technical Skills}

\subsection{Programming}
C, C++, Python, Bash

\subsection{Linux System Administration}

I have a strong grasp on how to set up and maintain personal Linux machines.

Please refer to \href{https://github.com/JaredDyreson/Thin-Mint}{this repository} for a detailed outline of my knowledge.

\section{References}

Available upon request.
\end{document}
